Question
========

The Cox proportional hazards regression model is a very popular model to describe 
survival or reliability data. The `pbc` data from the **survival** package will be used in this
example.

Write out the R code that will fit a Cox regression of survival time modeled on age, sex, cholesterol, albumin, 
stage (as a factor), billirubin, and the interaction of sex with cholesterol. 



```
library(survival)
coxph(Surv(time, status==2) ~ ____________, data = pbc)
```

To access the pbc dataset, you must first run `library(survival)`. This package in in-built, so
you don't have to install it. You can find the variable names in the data set by typing `help(pbc)`, which
will open the documentation for this dataset. I would like working R code, so please use the actual variable names
in your answer

Solution
========

```{r, echo = TRUE}
library(survival)
m1 <- coxph(Surv(time, status==2) ~ age + sex + chol + albumin + as.factor(stage) + 
    bili + sex:chol, data = pbc)
summary(m1)
```

```{r}
broom::tidy(m1)
```

Meta-information
================

extype: string
exname: coxreg
exsolution: nil
