Question
========


```{r initial-regression, echo=FALSE, fig.width=4, fig.asp=0.8}
library(tidyverse)
set.seed(3958)
D1 = tibble(x = rchisq(500, df=1)) %>% 
  mutate(y = 2 - 3*x + 5*x^2 + rnorm(500,0,2))
#write_csv(D1,  here::here('data/formative32_lm.csv'))
D1 <- D1 %>% mutate(x2 = x^2)
m1 = lm(y~x, data=D1)
plt <- ggplot(broom::augment(m1))+geom_point(aes(x = x, y = y)) + 
  geom_line(aes(x = x, y=.fitted), color='blue') + 
  theme_classic()
print(plt)
```


A data set imported and stored in the data.frame `D1` was used to fit a linear regression using the 
following code:

```{r, eval=FALSE}
lm(y~x, data=D1)
```

and the resulting regression line is plotted in blue. Obviously it isn't a very good fit, since it doesn't capture
the curvature in the x-y relationship well. 

Suggest another linear regression model that might fit the data better, of the form

```
lm(y ~ x + ______, data = D1)
```

The data is available [here](https://www.dropbox.com/s/f3hvv5t88m2hu5e/formative32_lm.csv?dl=1)

Solution
========

```{r final-regression, echo = TRUE}
lm(y ~ x + I(x^2), data = D1)
```

```{r,  fig.width=4, fig.asp=0.8}
m1 <- lm(y ~ x + I(x^2), data = D1)
ggplot(broom::augment(m1)) + 
  geom_point(aes(x = x, y = y)) + 
  geom_line(aes(x = x, y=.fitted), color='blue') + 
  theme_classic()
```

Meta-information
================

extype: string
exname: linreg1
exsolution: nil
