---
title: Selecting columns
author: Abhjit Dasgupta
output: 
    xaringan::moon_reader:
        css: [default, './robot.css', './robot-fonts.css', './sfah.css']
        #css: [default, metropolis, metropolis-fonts]
        nature:
            ratio: '16:9'
            highlightLanguage: "r"
            countIncrementalSlides: false
            highlightStyle: "zenburn"
            highlightLines: true
            slideNumberFormat: "%current%"
---

```{r setup, include=FALSE}
library(tidyverse)
weather_data <- read_csv('~/Dropbox/teaching/BIOF439/data/weather.csv')
weather1 <- weather_data %>% slice(1:3)
```



You can select columns by name or position, of course. 

```{r}
weather1 %>% select(year, element)
```

```{r}
weather1 %>% select(2, 4, 5)
```

> `weather1` is just a data.frame with the first 3 rows of the weather dataset

---

You can select consecutive columns 

```{r}
weather1 %>% select(d1:d14)
```
```{r}
weather1 %>% select(3:7)
```

---

You can also select columns based on some criteria in the column names.


```{r}
weather1 %>% select(starts_with("d"))
weather1 %>% select(ends_with('2')) 
```

> Whatever is in these selector functions `starts_with`, `ends_with`, etc., has to be quoted

---

You can select by column type

```{r}
weather1 %>% select(where(is.character))
weather1 %>% select(!where(is.numeric)) # Not numeric
```

---

There are several other options:

```{r, eval=F}
?tidyselect::language
```

.pull-left[

`:` for selecting a range of consecutive variables.

`!` for taking the complement of a set of variables.

`&` and `|` for selecting the intersection or the union of two sets of variables.

`c()` for combining selections.

In addition, you can use selection helpers. Some helpers select specific columns:

`everything()`: Matches all variables.

`last_col()`: Select last variable, possibly with an offset.
]

.pull-right[
These helpers select variables by matching patterns in their names:

`starts_with()`: Starts with a prefix.

`ends_with()`: Ends with a suffix.

`contains()`: Contains a literal string.

`matches()`: Matches a regular expression.

`num_range()`: Matches a numerical range like x01, x02, x03.

]

---

```{r, eval=F}
?tidyselect::language
```
.pull-left[

These helpers select variables from a character vector:

`all_of()`: Matches variable names in a character vector. All names must be present, otherwise an out-of-bounds error is thrown.

`any_of()`: Same as all_of(), except that no error is thrown for names that don't exist.

This helper selects variables with a function:

`where()`: Applies a function to all variables and selects those for which the function returns TRUE.


]
