```{r, echo=FALSE, results='hide'}
library(survival)
suppressPackageStartupMessages(library(tidyverse))
data(pbc)
library(broom)

m_cox <- veteran %>% 
  mutate(across(c(trt, celltype, prior), as.factor))%>% 
  coxph(Surv(time, status) ~ trt+age+karno+diagtime+prior, data=.)
fctrs <- m_cox$xlevels
out = tidy(m_cox, exponentiate = TRUE, conf.int = TRUE) %>% 
  mutate(ci = as.character(glue::glue('({round(conf.low, 4)},{round(conf.high,4)})')))

for(n in names(fctrs)){
  out <- out %>% mutate(term = str_replace(term, n, paste0(n, ' = ')))
}
out <- out %>% mutate(term = fct_rev(fct_inorder(term))) %>% 
  mutate(signif=ifelse(p.value <=0.05,'yes','no'))

plt <- ggplot(out, 
               aes(x = term, y = estimate, 
                   ymin = conf.low, ymax = conf.high))+
    geom_pointrange() + 
    geom_hline(yintercept = 1, linetype = 2)+
    theme_classic()+
    scale_color_manual('Significant?', values = c('yes'='red', 'no'='black'))+
    coord_flip()+
    labs(y = 'Hazard ratio', title='Cox regression results', caption='VA Lung Cancer study')
plt2 = ggplot(out, aes(x = term, y = 1, label = ci))+geom_text()+theme_void() + coord_flip()
```

Question
========

The following plot shows the results from a Cox proportional 
hazards regression of the Stanford Heart Transplant data. There are four predictors: age, year of the transplant, prior surgery (yes = 1, no = 0) and prior transplant (yes = 1, now = 0). The 95% confidence intervals are plotted for each hazard ratio. 

```{r, echo=FALSE, results = 'hide', fig.cap='', fig.width=6}
plt
```

Which of the predictors are statistically signficant?

> For those who don't know the duality of confidence intervals and p-values, in most cases,  significance at the 0.05 level is equivalent to the 95% confidence interval **not** covering the reference value.

Answerlist
----------

* trt
* age
* karno
* diagtime
* prior


Solution
=========

Answerlist
-----------

* FALSE. The confidence interval covers the reference value 1
* TRUE. The confidence interval doesn't cover the reference value 1
* FALSE. The confidence interval covers the reference value 1
* FALSE. The confidence interval covers the reference value 1
* FALSE. The confidence interval covers the reference value 1

Meta-information
================
extype: mchoice
exsolution: 01000
exname: eff1
