```{r, echo=F, results='hide'}
library(ggplot2)
library(RColorBrewer)
library(cowplot)

mytheme = theme_minimal()+
  theme(axis.title.y= element_text(angle=0, vjust=0.5),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())

d = tibble(x=factor(1:7), y=1)
plt1 <- ggplot(d, aes(x=x, y=y, fill=x))+
  geom_tile(width=0.5, height=0.5, show.legend = FALSE)+
  scale_fill_brewer(type='seq')+
  labs(x='', y = 'Sequential')+
  mytheme

plt2 <- ggplot(d, aes(x=x, y=y, fill=x))+
  geom_tile(width=0.5, height=0.5, show.legend = FALSE)+
  scale_fill_brewer(type='div')+
  labs(x='', y = 'Diverging')+
  mytheme

plt3 = ggplot(d, aes(x=x, y=y, fill=x))+
  geom_tile(width=0.5, height=0.5, show.legend = FALSE)+
  scale_fill_brewer(type='qual')+
  labs(x='', y = 'Qualitative')+
  mytheme
```

Question
========

The package **RColorBrewer** provides three types of color palettes

```{r, echo=F, fig.cap='', fig.height=2}
plot_grid(plt1, plt2, plt3, ncol=1, align='v')
```

Which type of palette would be most appropriate for a heatmap looking at over- and under-expression of genes in a sample relative to a control?

Answerlist
----------

* Sequential
* Diverging
* Qualitative

Solution
=========

Answerlist
----------

* FALSE. We want to see expressions that are too big and too small compared to the middle (no change). This palette would emphasize the over-expressed genes and hide the under-expressed genes
* TRUE
* FALSE. There is no ordering to this palette, and so it would visually not be clear which direction is which, and how the degree of over- or under-expression changed in each direction

Meta-information
================

exname: palette
extype: mchoice
exsolution: 010
